Create Regression Data

### 2022-05-02 data-cleaning/07-generate-frame-measures.Rmd
fix missing data

```{r}
# abortion cases
amicus <- box_read("947307207905", read_fun = readr::read_csv)
```

@@

sum_amicus %>% head()
```
```{r}
sum_amicus %>% filter(case == "Anders v Floyd" | case == "Ayotte v. PP")
```

>>>>

```{r}
# abortion cases
amicus <- box_read("947307207905", read_fun = readr::read_csv) %>% 
  mutate(brief_party = ifelse(id == 861815623586, 1, brief_party))
```

@@

sum_amicus %>% head()
```

### 2022-05-02 data-cleaning/08-create-regression-data.Rmd
fix missing data

```{r}
box_write(final,
          file_name = "amicus-iv-regression-data-frame-by-case-final-cases.csv",
          dir_id = 158993526875)
```

>>>>

```{r}
box_write(final,
          file_name = "amicus-iv-regression-data-frame-by-case-final-cases.csv",
          dir_id = 158993526875)
```
Pared down for review:

* women's frames (women's health, rights, future life, compulsory motherhood I and II, abortion regret)

* law frames (bad law, undue burden, overturn roe, privacy, standing, final authority)

* morality & religion

* evidence frames (evidence, uncertainty, untruthful)

```{r}
final_pared <- final %>% 
  rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x)) %>% 
  select(case:cirsplit,
         abortion_different,
         abortion_regret, womens_health, womens_rights, womens_future_life,
         compulsory_motherhood, compulsory_motherhood_ii,
         bad_law, undue_burden, overturn_roe, privacy, standing, final_authority,
         morality_religion,
         evidence, uncertainty, untruthful) %>% 
  filter(case != "Hartigan v Zbaraz") %>%
  filter(!is.na(justicevot)) %>% 
  select(-c(justiceid:justicefem)) %>% 
  select(case, ddate2, nonftyp2:cirsplit, sort(colnames(.))) %>% 
  distinct()
```

```{r}
box_write(final,
          file_name = "frame freq by case (pared).xlsx",
          dir_id = 158993526875)
```
